\section{Diffoscope}

This paper focuses on one of the tools being developed by
Reproducible Build project - \textbf{diffoscope}.
\textbf{diffoscope} is a tool for in-depth comparison of files, archives and
directories\cite{dfs}.
The motivation behind development of \textbf{diffoscope} was to have a tool
telling what exactly have changed between two builds by comparing 
their results. Therefore, main focus areas for this tool are:
\begin{itemize}
    \item Support for file formats that are used in build artifacts. \\
    Currently \textbf{diffoscope} supports various kinds of archives, packages,
    as well as some resources file formats, such as JSON data or PNG images.
    New file formats get constantly added by community.
    \item User-friendly output.\\
    Since the main goal of \textbf{diffoscope} is to provide users with a way to look
    into what makes two files different, its developers always try to
    improve the readability of output by hiding non-informative details and
    emphasizing the real differences.
\end{itemize}

\textbf{diffoscope} is free software licensed under the GNU General Public 
License version 3 or later. It is written in Python3 programming language.
It is available in the form of Debian package (unstable distribution), 
Python package (PYPI), Homebrew package, Arch Linux package. Source code
of \textbf{diffoscope} is also available from Git repository at \cite{dfs-git}. 
There is also an online version of \textbf{diffoscope} \cite{try-dfs}, so users 
can try this tool without installing it on their system.
Bugs and feature requests can be submitted and reviewed at Debian
bug tracking system \cite{dfs-bugs}.\\
Community of \textbf{diffoscope} developers can be describing as having
onion model \cite{aberdour2007achieving}.
The project is being developed constantly by number of dedicated 
developers and welcoming contributions as well as bug reports 
and feature requests from everyone. 
\textbf{diffoscope} development follows the Open Source Development Model 
\cite{osdm}, with frequent small releases and constant quality improvements.
These improvements are usually not planned in advance and often
done as result of resolving a bug or fulfilling a feature request.\\
In this paper, several improvements to \textbf{diffoscope} were implemented,
with focus on better support of various file formats and usability.
These improvements, too, were mostly dictated by bug and feature requests
received for \textbf{diffoscope}.



%\cleardoublepage
