\section{Reproducible Builds for Open-Source Software}
\nomenclature{FUSE}{Filesystem in Userspace}
\nomenclature{Tor}{Free software for enabling anonymous communication}

\subsection[Motivation and history]{Motivation and history}
\nopagebreak[4]{
With the increasing popularity of open-source software \autocite{Anthes16a} and its adoption in large
scale systems, the security and quality assurance of that software becomes a
high-priority question. Commercial closed-source software projects rely on
internal quality assurance methods, and users of their products are expected
to trust results of such assurance. While it is a working model for many
companies, it may lead to cases when known or deliberately introduced flaws
in software are hidden from end-user, the most known example being 2015
Volkswagen emissions scandal \autocite{Sch15}. \\\\
FOSS, on the other hand, uses completely different
approach. While there is often no person directly responsible of quality assurance,
publicly available source code means that every interested user or company using
that software, may examine the code for potential flaws, therefore assuring
quality for themselves \autocite{hoepman2007increased}.
That model assumes that the source code ultimately defines the software product.
However, in reality people usually use software products in forms of binaries,
compiled libraries or other form of build artifacts, which are the results of software build
process. In fact, it is more common for users to obtain software products in
form of build artifacts distributed by someone who built it, rather than
acquiring the source code and building it for themselves. \\\\
That consideration brings forth certain questions. Is the source code really the only
thing that defines the output of a software building process? Do other factors,
such as the configuration of the build system, affect it? How can we be sure these
factors do not cause modification of the resulting binary? If the binary gets modified by varying build environment, then just ensuring the source code does not have any flaws does
not guarantee the resulting binary does not have them, since these flaws could be introduced,
whether intentionally or not, by a build system. \\\\
Open-source projects that place an extra emphasis on security
and privacy are especially concerned with this possibility, as
it may leave the products they are building vulnerable to cyberattacks.
The Tor project was one of the first projects to ring the alarm in the 2013, alerting others of the problem and taking first steps
in ensuring what soon would be named reproducible builds \autocite{tor13, tor14}.
Since then, a lot of free software projects acknowledged the problem and
tried to come up with a solution. Individual projects concerned with quality
assurance of software they are producing started researching possible sources of
non-determinism in build process as well as ways to remove them, as can be
seen on example of TrueCrypt \autocite{de2014challenges}.\\\\
An important role in the following actions taken to raise awareness of the
problem was played by Debian, one of the most popular Linux distributions.
Over the last two years, members of Debian community gathered these efforts
under the flag of the project called Reproducible Builds \autocite{rb},
gave numerous talks on technical conferences on the matter
\autocite{Lun14, lca2017_valerie}, and organized
two summits dedicated to problem of reproducible builds. They also set up a continuous
testing infrastructure \autocite{tests-rbo}, which checks reproducibility
of Debian packages, and designed several tools helping to find
differences between build artifacts and identify common issues leading to
unreproducible builds.}
\subsection[Definitions]{Definitions}
\nopagebreak[4]{
Representatives of projects taking part in the Reproducible Builds effort
agreed on following definition of reproducible build \autocite{rb-def}:
\theoremstyle{definition}
\begin{definition}{Reproducible build.} \\
A build is reproducible if given the same source code, build environment and build
instructions, any party can recreate bit-by-bit identical copies of all specified artifacts.
\\
\\
The relevant attributes of the build environment, the build instructions and the source
code as well as the expected reproducible artifacts are defined by the authors or
distributors. The artifacts of a build are the parts of the build results that are the
desired primary output.
\end{definition}


The following terms are used in this definition \autocite{rb-def}:
\begin{itemize}
    \item \textit{Source code} is usually a checkout from version control at a
    specific revision or a source code archive.

    \item \textit{Relevant attributes of the build environment} would usually include
    dependencies and their versions, build configuration flags and environment
    variables as far as they are used by the build system (e.g. the locale).
    It is preferable to reduce this set of attributes.

    \item \textit{Artifacts} would include executables, distribution packages or
    filesystem images. They would not usually include build logs or similar ancillary
    outputs.

    \item The reproducibility of artifacts is verified by \textit{bit-by-bit} comparison.
    This is usually performed using cryptographically secure hash functions.

    \item Authors or distributors means parties that claim \textit{reproducibility} of
    a set of artifacts. These may be upstream authors, distribution maintainers or any
    other distributor.
\end{itemize}

It can be seen from the definition that reproducibility is an attribute of a software product as a whole, as it is affect the build process, that is the link between the source code and the distributed binaries. If the software builds into different binaries when built twice, one cannot assume one of the versions is ``right'' and another one is ``wrong'' -- instead, it can be concluded that the whole software has reproducibility issue that needs to be resolved by altering either the source code or the predefined way this software is built.\\\\

As described in the documentation section of \autocite{rb}, it is not realistically possible, or desirable, to mandate that the same source code is turned into the same sequence of bytes in all situations. The output of a compiler is likely to be different from one version to another as better optimizations are integrated all the time. 
Instead, reproducible builds happen in the context of a build environment. It usually comprises the set of tools, required versions, and other assumptions about the operating system and its configuration. A description of this environment should typically be provided alongside any distributed binary package.
}
\subsection[Testing reproducibility]{Testing reproducibility}
In practice, reproducibility is tested using the following procedure:
\begin{itemize}
    \item The software is built from the provided source the first time, and the result is saved.
    \item Some variations are introduced into the build environment.
    \item Build the software the second time from the same sources.
    \item Compare the results. If they are bit-by-bit identical, it can be assumed the software is reproducible with respect to the introduced variations.
    \item If the results are not identical, specific tools can be used to find out what exactly has changed between them, therefore helping to identify the underlying reproducibility issue.
\end{itemize}

The list of variations used by the Reproducible Builds project in the testing process includes 
    date and time,
    build path,
    hostname,
    domain name,
    filesystem,
    environment variables,
    timezone,
    language,
    locale,
    user name,
    user id,
    group name,
    group id,
    kernel version,
    umask,
    CPU type and number of CPU cores.


\subsection[Tools]{Tools}
\nopagebreak[4]{

A number of tools were designed by the Reproducible Builds community to help software
projects check their products for reproducibility, find out what gets changed between
two builds, identify and fix common unreproducibility issues.
\begin{itemize}
    \item \textit{diffoscope} is a tool for in-depth comparison of files, archives,
          and directories. In content of reproducibility testing, it is usually used on build artifacts to find what exactly is different between them, allowing for easier identification of reproducibility issues.
    \item \textit{trydiffoscope} is an online version of diffoscope. It can be used to compare files without installing diffoscope with all its dependencies.
    \item \textit{disorderfs} is an overlay FUSE (Filesystem in Userspace) filesystem that deliberately introduces non-determinism into filesystem metadata. Since quite a few reproducibility issues are related to the filesystem specifics -- e.g. file order -- disorderfs can be used to identify these issues.
    % TODO: check this
    \item \textit{strip-nondeterminism} is a library for stripping non-deterministic information, such as timestamps and file system order, from files. Usage of strip-determinism in the build process can be used to achieve reproducibility. However, it is designed as a quick fix tool, not as a permanent solution. In general, it is preferred that the software handles reproducibility issues internally, without resorting to a third-party tool every time it is built.
    \item \textit{reprotest} is a tool for building the same source code under different environments to check if these changes led to changes in the resulting binaries. \textit{reprotest} builds the same source code twice in different environments, and then checks the binaries produced by each build for differences. If any are found, then diffoscope is used to display them in detail for later analysis.
\end{itemize}

The Reproducible Builds project members have also come up with a \texttt{SOURCE\_DATE\_EPOCH} specification \autocite{SDEspec} to deal with reproducibility issues arising from the usage of timestamps in the build process.
These issues arise when software packages embed compile-time timestamps into generated files. As the current time changes between builds, this approach leads to the differences in the binaries' contents. \\\\
The idea behind the \texttt{SOURCE\_DATE\_EPOCH} proposal is to modify build process of the software to use the environment variable \texttt{SOURCE\_DATE\_EPOCH} instead of the current time if that environment variable is set. 
That proposal was adopted by several build tools and individual packages\autocite{SDEproposal}, significantly decreasing the number of software packages affected by timestamp-related reproducibility issues.\\


}




%\cleardoublepage
